Evidence of the necessity of isotopic precise calculation in fuel cycle calculation

### 2016-07-01 paper.tex
correction on depletion discussion

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{decay_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
    using the 3 prediction models: ``fix mixing ratio'' (``fix'', blue),
    ``Pu-equivalent'' (``Pu-eq'', green) and ``Neural Network'' (``NN'', red),
    with (plain line) and without (dash line) decay enable.} 
  \label{fig:d}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{irradiation_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
    using the ``Neural Network'' prediction models, using recipe based spent
    fuel composition (red) and recalculated spent fuel composition (orange),
    with (plain line) and without (dash line) decay enable.}
  \label{fig:depletion}
\end{figure}

%% PPHW: - I don't know which answer is which !?!?  bad legend labels!

%% PPHW: I don't know what the difference between these calculations is!!!
%% You have 4 results but haven't made clear what the variations are. Do they
%% all have decay?  I think the following is correct, but I'm not sure...

@@

This is caused by the slight change in the composition in the available plutonium
(see Fig. \ref{fig:depletioncompo}): in the case of the depletion calculation
the available plutonium contain $68\%$ of $^{239}$Pu versus $64\%$ in the recipe
based case, and also significantly less $^{241}$Pu leading to less $^{242}$Pu in
the cycle. The amounts of the other nuclides are very close.

>>>>

\begin{figure}[h!] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{decay_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
    using the 3 prediction models: ``fix mixing ratio'' (``fix'', blue),
    ``Pu-equivalent'' (``Pu-eq'', green) and ``Neural Network'' (``NN'', red),
    with (solid line) and without (dash line) decay enable.} 
  \label{fig:d}
\end{figure}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.48\textwidth]{irradiation_pu_contribution.png}
  \caption{Evolution of the fraction of plutonium in the fresh PWR-MOX fuel
    using the ``Neural Network'' prediction models, using recipe based spent
    fuel composition (red) and recalculated spent fuel composition (orange),
    with (solid line) and without (dash line) decay enable.}
  \label{fig:depletion}
\end{figure}

@@

This is caused by the slight change in the composition in the available
plutonium (see Fig. \ref{fig:depletioncompo}): in the case of the depletion
calculation the available plutonium contain $68\%$ of $^{239}$Pu versus $64\%$
in the recipe based case, and also less $^{242}$Pu and $^{241}$Am, respectively
$4.8\%$ and $5.4\%$ in the depletion case versus $7.3\%$ and $6.7\%$. The
amounts of the other nuclides are very close.
